---
title: "Milestone 8"
author: "Margaret Butler"
date: "11/21/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(gutenbergr)
library(tidyverse)
library(stringr)
library(fs)
library(scales)
library(lubridate)
library(dplyr)
library(knitr)
library(tibble)
library(foreign)
library(readr)
library(janitor)
library(tibble)
library(purrr)
library(ggplot2)
library(ggrepel)
library(tidytext)

## load packages

```
## Looking at Gothic Literature

Downloading books I want to look at from the gutenbergr package. Books I am looking at in this are *Frankenstein*, *The Strange Case of Dr. Jekyll and Mr. Hyde*, *Carmilla*, *The Phantom of the Opera*, and *Dracula*.

## Gutenberg Book ID Numbers

1. Frankenstein 84
2. The Strange Case of Dr. Jekyll and Mr. Hyde 43
3. Carmilla 10007
4. The Phantom of the Opera 175
5. Dracula 345

```{r, inclue=FALSE, message=FALSE}

gothic <- gutenberg_download(c(84, 43, 10007, 175, 345))

frankenstein <- gutenberg_download(84)
jekyllhyde <- gutenberg_download(43)
carmilla <- gutenberg_download(10007)
phantom <- gutenberg_download(175)
dracula <- gutenberg_download(345)

## downloading the books into one big data set and then into separate data sets

tidy_gothic <- gothic %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_frankenstein <- frankenstein %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_jekyllhyde <- jekyllhyde %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_carmilla <- carmilla %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_phantom <- phantom %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

tidy_dracula <- dracula %>%
  unnest_tokens(word, text) %>%
  anti_join(stop_words)

## tidying words so I can pick through them at my leisure

```

New R chunk so that I dont have to reload the data as I play with it

```{r}

tidy_gothic %>% 
  count(word, sort = TRUE)
  
## checking the most common words across all five texts

```

*The Phantom of the Opera* skews the data because Christine and Raoul are in the top ten most frequent words! Moving on to look at each book individually.

Have just discovered that gutenbergr does not count pronouns or articles in its word count which is tragic because I want to look at pronoun usage!!

```{r}

tidy_frankenstein %>% 
   count(word, sort = TRUE)

tidy_jekyllhyde %>% 
  count(word, sort = TRUE)

tidy_carmilla %>% 
  count(word, sort = TRUE)

tidy_dracula %>% 
  count(word, sort = TRUE)

tidy_phantom %>% 
  count(word, sort = TRUE)

```

Time is in the top ten for all of them except for in Jekyll and Hyde.

```{r}

dir_create("gothic_app")

write_rds(tidy_gothic, "gothic_app/tidy_gothic.rds")

## made dirctory for gothic shiny app and made file to use in said shiny app

```


